\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{tasks}
\usepackage{multicol}

% Configure href boxed bod coloring 
\hypersetup{ 
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    filecolor=black
}
% Formatting sections
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{*0}{*0}

\begin{document}

\begin{center}
    {\LARGE Emmanuel Walker} \\[5pt]
    \href{mailto:walkeremmanuel33@gmail.com}{walkeremmanuel33@gmail.com} | (719) 453-9549 | Mundelein, IL %| \href{https://linkedin.com/in/enwalker33}{LinkedIn.com/in/enwalker33}
\end{center}

\section{Summary}
Dynamic Systems Test Engineer with 5 years of experience in systems testing and administration, specializing in Linux
and Windows Operating Systems. Proven expertise in developing and executing procedures, integrating compliance
measures, and utilizing tools for process monitoring. Seeking Systems Engineer role to leverage strong skills in system
architecture, test plan development, and process automation.
\section{Work Experience}

\subsection{Northrop Grumman}
\noindent\textbf{Systems Engineer} \hfill \textit{Jan 2024 - Oct 2024} \\
Northrop Grumman is a leading aerospace and defense company that develops advanced technology solutions for government clients, specializing in security, defense, and space systems.
\begin{itemize}[leftmargin=*]
    \item Led a team of engineers to execute component and full systems tests on Linux and Windows platforms.
    \item Developed and maintained test scenarios and procedures for security testing and auditing.
    \item Collaborated with engineering teams to integrate security measures into Test Readiness Review presentations.
    \item Developed test procedures for PCB circuit assemblies, ensuring alignment with engineering specifications and quality standards.
    \item Conducted comprehensive system specification verification analyses to validate compliance with customer requirements.
\end{itemize}

\subsection{Cold Start Rentals, LLC}
\noindent\textbf{Owner} \hfill \textit{Dec 2021 - Dec 2024} \\
Cold Start Rentals, LLC was a rental company specializing in providing equipment for short-term and long-term use.
\begin{itemize}[leftmargin=*]
    \item Spearheaded the establishment and strategic growth of Cold Start Rentals, LLC, overseeing all aspects of business operations including financial management, marketing, client relations, and service delivery to drive company success and profitability.
    \item Established and strategically grew a rental business, overseeing comprehensive operations including financial
management, marketing, client relations, and service delivery.
    \item Managed business operations to enhance company success and profitability.
\end{itemize}

\subsection{Aston Carter}
\noindent\textbf{Financial Service Representative} \hfill \textit{Mar 2022 - Aug 2022} \\
Aston Carter is a professional staffing agency that placed financial service representatives at T. Rowe Price, a global
investment management firm specializing in mutual funds, retirement planning, and 529 college savings plans.
\begin{itemize}[leftmargin=*]
    \item Facilitated services related to T. Rowe Price’s 529 college savings plans, retirement accounts, and life insurance, enhancing client understanding of financial products and services.
    \item Analyzed financial data to provide clients with clear insights, aiding in informed decision-making.
    \item Communicated complex financial information effectively, contributing to improved client financial literacy and
    satisfaction.
    
\end{itemize}


\subsection{AT\&T}
\noindent\textbf{Sales Consultant} \hfill \textit{Nov 2020 - Dec 2021} \\
AT&T is one of the largest telecommunications providers in the world, offering enterprise communication,
broadband, and mobile solutions.
\begin{itemize}[leftmargin=*]
    \item Facilitated customer retention by effectively communicating product value and fostering strong client relationships.
    \item Enhanced customer satisfaction and loyalty through personalized engagement and relationship-building strategies.
\end{itemize}

\subsection{Inpriva, Inc}
\noindent\textbf{System Administrator} \hfill \textit{Aug 2019 - Oct 2020} \\
Inpriva, INC is a healthcare IT company specializing in secure messaging and compliance solutions for healthcare
providers, ensuring HIPAA and HITRUST-compliant data exchange.
\begin{itemize}[leftmargin=*]
\item Managed enterprise IT infrastructure, including Active Directory, DNS, DHCP, Group Policy Objects, and Nginx
Server on Linux OS for web hosting, while analyzing, communicating, and resolving technical issues for internal
and external clients.
\item Utilized SPLUNK SIEM to monitor and analyze system logs for security threats, and developed dashboards for
system performance using Splunk’s Query Language (SplunkQL).
\item Provided technical support to internal teams and external clients, ensuring secure and compliant system operations.
\item Ensured compliance with IT security policies, supporting healthcare data protection initiative.
\end{itemize}

\section*{Education}
\begin{tabular}{@{}l@{\hspace{2cm}}r@{}}
    \textbf{Bachelor of Science in Business Administration} & \textsc{concentration:} \textbf{Information Systems} \\
\textit{Colorado State University} & \textbf{2016 - 2020}
\end{tabular}
\section{Certifications}
\textbf{CompTIA Security+ CE} \hfill \textit{Feb 2023}

\section*{Skills}

% Set default itemize parameters for uniform spacing and indentation.
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=0pt, label=\textbullet}

% \begin{multicols}{3}
\begin{itemize}
    • IT Systems Administration • IT Systems Integration • IT Systems Security 
    • IT Systems Monitoring • IT Systems Maintenance • IT Systems Troubleshooting 
    • IT Systems Deployment • IT Systems Optimization • IT Systems Upgrades 
    • IT Systems Backup and Recovery • IT Systems Documentation • IT Systems Support 
    • Systems Architecture • Enterprise Architecture • Network Configuration 
    • DNS • DHCP • Nginx • Database Management • Process Automation 
    • Scripting Languages: Bash • PowerShell • Python • JavaScript 
    • Web Development: HTML • CSS • SQL 
    • Tools: Splunk • Active Directory • Windows • Linux 
    • API • SaaS • PaaS • CRM • SIEM • SAP ERP 
    • Enterprise Miner • Data Analysis • Excel 
    • DOD Test Methodologies • Test Scripts Development and Execution 
    • Test Scenarios • Product Design Reviews • Test Plan Development 
    • Black Box Testing • White Box Testing • Regression Testing 
    • Functional Testing • System Testing • Manual Testing 
    • UI Automation Testing • Verification \& Validation Testing 
    • Teamwork • Problem Solving • Organization • Communication • Time Management
\end{itemize}
% \end{multicols}

\end{document}

